### 2017-06-17 paper.tex
Fix grammatic usage of open source

Lessons take significant effort to build,
and even more effort to maintain.
The collaborative code development methods pioneered by the open source community
offer a way forward,
allowing us to create lessons which are open,
accessible,
and continually updated and improved by a community of contributors.
This paper provides ten simple rules that can help others create sustainable lessons.

@@

Lessons take significant time and energy to build and even more effort to maintain.
Collaborative lesson development refers to the combined efforts of teachers to build and maintain lessons.
By leveraging a community approach, educational resources can be more sustainable, robust, and responsive.
When lessons are created in an open source community, all lessons are open and accessible,
and they can be continually updated and improved by a community of contibutors.

Despite the proven success of open-source and collaboratively developed lesson plans,
it is surprisingly uncommon in the traditional accademic setting.
Each year, thousands of university lecturers teach subjects ranging from first year biology,
to graduate-level courses in Indian film.
Some might use a common textbook written by a single author or two,
but besides that lecturers develop and improve their course materials in isolation.
It is staggering to think how many wheels are being re-invented,
how much valuable time has been wasted,
and ultimately how the progress of tertiary education has been held back by
the lack of community collaboration and sharing in this process.
This problem obviously extends beyond the university sector,
but it is curious that it is endemic in tertiary education,
given that research depends so critically on collaboration and sharing,
and that most researchers complain about how much time teaching takes away from research.

The authors collectively have experience with community-developed lesson plans
in the context of research computing in the sciences and humanities.
They primarily draw on their experiences with pedagogical organizations such as
Software Carpentry and Programming Historian.
Software Carpentry was founded in 1998 to teach scientists basic computing skills,
and has since spawned two sibling organizations called Data Carpentry and Library Carpentry.
Programming Historian was founded in 2008,
and has evolved into a collaboratively-edited site providing lessons to humanists.
These organizations have been successful in adapting open source development methods
to lesson development and maintenance.
Their guiding principles are that lessons should be:

@@

Tools can help,
especially if they allow proposed changes to be viewed and discussed
prior to their incorporation/merger into the lessons
(in open source software development this is known as ``pre-merge review'').
Providing a gentle on-ramp for new contributors is essential,
but some tools come with a considerable up-front learning curve.
Housing lessons on GitHub with changes suggested via pull requests is 
ideal for pre-merge review, for instance,
but it requires contributors to know how to use Git,
which has a notoriously steep learning curve \cite{git-survey}.
Allowing people to edit a Google Doc or Wiki-based editing does not offer pre-merge review,
but the low barrier to entry can help get conversations started.

@@

But sometimes choices must be made.
The open source software community has wrestled with these issues for three decades,
and has evolved some best practices to handle them
\cite{producing-oss}.
As discussed in Rule~5,
the first step is to have a clear governance structure and a clear, permissive license.
Minor disagreements should be discussed openly and respectfully.
If they cannot be resolved---i.e., if they turn out not to be so minor after all---then
contributors should split off and evolve the lesson in the way they see best.
(This is one of the reasons to have a permissive license.)

>>>>

Lessons take significant effort to build,
and even more effort to maintain.
The collaborative code development methods pioneered by the open-source community
offer a way forward,
allowing us to create lessons which are open,
accessible,
and continually updated and improved by a community of contributors.
This paper provides ten simple rules that can help others create sustainable lessons.

@@

Lessons take significant time and energy to build and even more effort to maintain.
Collaborative lesson development refers to the combined efforts of teachers to build and maintain lessons.
By leveraging a community approach, educational resources can be more sustainable, robust, and responsive.
When lessons are created in an open-source community, all lessons are open and accessible,
and they can be continually updated and improved by a community of contibutors.

Despite the proven success of open source and collaboratively developed lesson plans,
it is surprisingly uncommon in the traditional accademic setting.
Each year, thousands of university lecturers teach subjects ranging from first year biology,
to graduate-level courses in Indian film.
Some might use a common textbook written by a single author or two,
but besides that lecturers develop and improve their course materials in isolation.
It is staggering to think how many wheels are being re-invented,
how much valuable time has been wasted,
and ultimately how the progress of tertiary education has been held back by
the lack of community collaboration and sharing in this process.
This problem obviously extends beyond the university sector,
but it is curious that it is endemic in tertiary education,
given that research depends so critically on collaboration and sharing,
and that most researchers complain about how much time teaching takes away from research.

The authors collectively have experience with community-developed lesson plans
in the context of research computing in the sciences and humanities.
They primarily draw on their experiences with pedagogical organizations such as
Software Carpentry and Programming Historian.
Software Carpentry was founded in 1998 to teach scientists basic computing skills,
and has since spawned two sibling organizations called Data Carpentry and Library Carpentry.
Programming Historian was founded in 2008,
and has evolved into a collaboratively-edited site providing lessons to humanists.
These organizations have been successful in adapting open-source development methods
to lesson development and maintenance.
Their guiding principles are that lessons should be:

@@

Tools can help,
especially if they allow proposed changes to be viewed and discussed
prior to their incorporation/merger into the lessons
(in open-source software development this is known as ``pre-merge review'').
Providing a gentle on-ramp for new contributors is essential,
but some tools come with a considerable up-front learning curve.
Housing lessons on GitHub with changes suggested via pull requests is 
ideal for pre-merge review, for instance,
but it requires contributors to know how to use Git,
which has a notoriously steep learning curve \cite{git-survey}.
Allowing people to edit a Google Doc or Wiki-based editing does not offer pre-merge review,
but the low barrier to entry can help get conversations started.

@@

But sometimes choices must be made.
The open-source software community has wrestled with these issues for three decades,
and has evolved some best practices to handle them
\cite{producing-oss}.
As discussed in Rule~5,
the first step is to have a clear governance structure and a clear, permissive license.
Minor disagreements should be discussed openly and respectfully.
If they cannot be resolved---i.e., if they turn out not to be so minor after all---then
contributors should split off and evolve the lesson in the way they see best.
(This is one of the reasons to have a permissive license.)
